### 2021-04-19 README.Rmd
added badge back to readme

<!-- badges: start -->
<!--[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)-->
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
<!-- badges: end -->
